---
title: "feitosa_leonardo_a4_task3"
author: "Leonardo Feitosa"
date: "01/03/2021"
output: 
  html_document:
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(boot)
library(patchwork)
```


## Create data
```{r}
values <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)

values_df <- data.frame(values)
```

```{r, include = FALSE}
# Boolean test
values == 1


values_prop <- mean(values == 1)
values_prop
```

## Exploratory analysis
```{r}
hist(values_df$values)

mean(values_df$values)

t.test(values_df$values)
```


## Create function
```{r}
prop_fun <- function (x, i) {mean(x[i])}

values_vec <- values_df$values

gender_boot_100 <- boot(values,
                        statistic = prop_fun,
                        R = 100)

gender_boot_10k <- boot(values,
                        statistic = prop_fun,
                        R = 10000)
```

```{r}
# Outputs of both bootstrap resamples
gender_boot_100

gender_boot_10k
```



## Create data frames
```{r}
gender_boot_100_df <- data.frame(bs_prop = gender_boot_100$t)
gender_boot_10k_df <- data.frame(bs_prop = gender_boot_10k$t)
```

## Plot histogram
```{r, message = FALSE}
ggplot(data = gender_boot_10k_df, aes(x = bs_prop)) +
  geom_histogram() +
  theme_bw()
```

## Calculate the confidence interval
```{r}

boot.ci(gender_boot_10k, conf = 0.95)
```

The proportion of UCSB students who reported some kind of exclusionary, hostile or intimidating experience at the university and that self-report and nonbinary/genderqueer is 61% (n = 36), with a 95% bootstrap confidence interval of [44.4, 78.0] (n = 10,000 bootstrap samples).






















